### 2016-06-23 sec7_experiment.tex
Lets fix sec 6!!
aaaaa

@@

\subsection{Performance Comparison}
Since the both TRPM and SPARE utlizes pruning rules that related to the 
pattern parameters $M$,$L$,$G$,$K$. It is interesting to
see the performance of TRPM and SPARE under different parameter settings.
%\textbf{Default Setting}: We now analyze the TRPM and SPARE algorithm under different
%parameter settings. Under the default parameter settings,
%the performance of TRPM and SPARE is shown as in the 
%following table:
%\begin{table}
%\small
%\begin{tabular}{|c|c|c|c|c|c|c|}
%\hline 
%Data Set& \multicolumn{2}{c|}{TRPM} & \multicolumn{2}{c|}{SPARE} & \# Patterns \\ 
%\hline 
% & Map-Shuffle & Reduce & Map-Shuffle & Reduce &  \\ 
%\hline 			
%Shopping &55 & 279 & 183 &414 &369\\ 
%\hline
%GeoLife &72 & 408 & 162 &585 &441  \\
%\hline
%Taxi &193 & 619 & 562 &3086 &585 \\
%\hline 
%\end{tabular} 
%\caption{Detail performance of TRPM and SPARE under default parameters.}
%\end{table}
%
%As can be seen from the above table, the number of patterns
%discovered by the default parameters are up to five hundreds.
%Thus, the parameter settings are reasonable. Besides, we 
%can see that TRPM suffers from shuffle and mining process. 
%This is because $\eta$ is set to be $309$ under default parameters.
%As a comparison, SPARE takes only in average
% 36\% of TRPM's shuffle time. 
%To study the performance of TRMP and SPARE, we run both algorithms 
%in all three datasets under different parameter settings. 
We run both of the two algorithms in all three dataset and report
their overall performances as in Figures~\ref{exp:performance_vary}.
In brief, both algorithms are able to handle the large-scaled real
datasets. However, we observe that TRMP's performance largely depends
on the pattern parameters. In cases when $G$ is large, 
TRMP takes near three hours (e.g., in Taxi dataset).
In contrast, SPARE performs quite stable. Another general observation
is that both algorithms run slower in the Taxi dataset as compared to
other two datasets. This is because Taxi dataset contains
the most number of temporal data points, which is around 7 times of Shopping
dataset and 5 times of geolife dataset. We observe that, 
in almost all cases, SPARE outperforms TRMP and analyze the detail
of each scenario separately.

@@

\subsubsection{Detail comparison between SPARE and TRPM}

\subsection{SPARE Analysis}

\subsubsection{Scalability}
\begin{figure}[h]
\centering
   \includegraphics[width=0.45\textwidth]{/exp/spare/scalability.eps}
\caption{Scalability of SPARE vary. $N$ under different datasets.}
\label{exp:patterns_vary}
\end{figure}

\subsubsection{Load Balance}

>>>>

\textbf{Algorithms}: We implement TRPM, SPARE and SPARE+ for comparison study. TRPM and SPARE are implement as described in Section 4 and 5. In SPARE+, we hook an additional load balance stage to the map phase. When the map phase completes, SPARE+ collects the size of stars from all mappers. Then we use the best-fit strategy for task allocation. In best-fit, tasks are assigned in decreasing order of 
their sizes, and the biggest unassigned task is allocated to the current most empty reducer. Our task size is estimated on the edges of stars, that is we try to balance the edges processed by each reducers.

@@

\subsection{Performance Comparison}
Since the both TRPM and SPARE utilizes pruning rules that related to the 
pattern parameters $M$,$L$,$G$,$K$. It is interesting to
see the performance of TRPM and SPARE under different parameter settings.
%\textbf{Default Setting}: We now analyze the TRPM and SPARE algorithm under different
%parameter settings. Under the default parameter settings,
%the performance of TRPM and SPARE is shown as in the 
%following table:
%\begin{table}
%\small
%\begin{tabular}{|c|c|c|c|c|c|c|}
%\hline 
%Data Set& \multicolumn{2}{c|}{TRPM} & \multicolumn{2}{c|}{SPARE} & \# Patterns \\ 
%\hline 
% & Map-Shuffle & Reduce & Map-Shuffle & Reduce &  \\ 
%\hline 			
%Shopping &55 & 279 & 183 &414 &369\\ 
%\hline
%GeoLife &72 & 408 & 162 &585 &441  \\
%\hline
%Taxi &193 & 619 & 562 &3086 &585 \\
%\hline 
%\end{tabular} 
%\caption{Detail performance of TRPM and SPARE under default parameters.}
%\end{table}
%
%As can be seen from the above table, the number of patterns
%discovered by the default parameters are up to five hundreds.
%Thus, the parameter settings are reasonable. Besides, we 
%can see that TRPM suffers from shuffle and mining process. 
%This is because $\eta$ is set to be $309$ under default parameters.
%As a comparison, SPARE takes only in average
% 36\% of TRPM's shuffle time. 
%To study the performance of TRMP and SPARE, we run both algorithms 
%in all three datasets under different parameter settings. 
We run both of the two algorithms in all three dataset and report
their overall performances as in Figures~\ref{exp:performance_vary}.
In brief, both algorithms are able to handle the large-scaled real
datasets. However, we observe that TRMP's performance largely depends
on the pattern parameters. In cases when $G$ is large, 
TRMP takes near three hours (e.g., in Taxi dataset).
In contrast, SPARE performs quite stable. Another general observation
is that both algorithms run slower in the Taxi dataset as compared to
other two datasets. This is because Taxi dataset contains
the most number of temporal data points, which is around 7 times of Shopping
dataset and 5 times of geolife dataset. We observe that, 
in almost all cases, SPARE outperforms TRMP and analyze the detail
of each scenario separately.

@@

%\subsubsection{Anatomy of SPARE and TRPM}

\subsection{SPARE Analysis}
Since SPARE is superior than TRPM, we further study the \emph{load balance} and \emph{scalability} of SPARE.

\subsection{Pruning Power}

\subsubsection{Load Balance}
We first compare SPARE and SPARE+ by analyzing the running time at
each map-reduce stage. The detail anatomy is shown in Figure~\ref{}

To further study the superior performance of SPARE+, we compare load distribution from all executors. We display the result in Figure~\ref{}.

\subsubsection{Scalability}
We then test the performance of SPARE under different number of executors. The result on the three dataset is presented in Figure~\ref{exp:scalability}. We can see from the Figure that SPARE achieves good scalability under all three cases. For instance, for Taxi dataset, when the executors rises from 14 to 54, the performance improves 3.5 times which is almost linear to the increase of executors. Such a pattern also holds for other two datasets.

\begin{figure}[h]
\centering
   \includegraphics[width=0.45\textwidth]{/exp/spare/scalability.eps}
\caption{Scalability of SPARE vary. $N$ under different datasets.}
\label{exp:scalability}
\end{figure}
